

\chapter*{Acknowledgements}
\addcontentsline{toc}{chapter}{Acknowledgements}

I want to thank the following people for their help in making this thesis a reality.

For their expert guidance, and their patience and kindness, my supervisors Mark and Matias.

And for their moral support in many different ways:
Lucia, Steven, Sara, my siblings Pieter and Silke, my mom and dad, and my friends in Holsbeek (Lies, Emily, Koen, Tim, Arnoud, Katia) and in Nottingham (Frederica, Helen, Emily).
Without them, this thesis would have never been.


\chapter*{Code availability}
\addcontentsline{toc}{chapter}{Code availability}

Figures and tables in this thesis are often accompanied by a link to the Jupyter Notebook that generated them. These notebooks contain more information than can be conveyed in just the caption. These links look like, e.g:
\nburl{2021-12-06__local_HH_dV_shape}.
To visit these links, in the digital version of this document, just click them. In the paper version, convert them to an URL, following this example: {\small \url{https://tfiers.github.io/phd/nb/2021-12-06__local_HH_dV_shape.html}}.

The Jupyter notebooks almost always rely on functions developed in previous notebooks, and factored out to separate files. These files can be found at \url{https://github.com/tfiers/phd} (under the \texttt{pkg/} subdirectory). This GitHub repository is currently private, but the reader will be granted access after sending their GitHub email or username to \texttt{tomas.fiers@gmail.com}.
